Post-replication citation patterns in psychological science: Preliminary analysis

### 2020-07-20 analysis/preliminaryAnalysis.Rmd
text changes
minor text edits

Firstly, we'll plot raw citation curves for the five cases to get a flavour of what we are working with. The x-axis starts in the year the target study was published. The black arrow indicates the publication date of the contradictory replication study. The black line represents the raw annual citation count to the target article. Note that the citation data was acquired on April 26th, 2019, which partly contributes to the fall in citations in 2019 in all cases.

@@

There seems to be evidence of citation bias (citing the target article but not the replication) in all cases, though the effect size smaller in the Sripada case (probably because this study is probably only well known because of its connection to the Baumeister study - recall that it was used as a methodological proxy for that more influential study in the replication attempt).

>>>>

Firstly, we'll plot raw citation curves for the five cases to get a flavour of what we are working with. The x-axis starts in the year the target study was published. The black arrow indicates the publication date of the contradictory replication study. The black line represents the raw annual citation count to the target article. Note that the citation data was acquired from the WOS database on April 26th, 2019, which partly contributes to the fall in citations in 2019 in all cases.

@@

There seems to be evidence of citation bias (citing the target article but not the replication) in all cases, though the effect is smaller in the Sripada case (probably because this study is probably only well known because of its connection to the Baumeister study - recall that it was used as a methodological proxy for that more influential study in the replication attempt).
